Figure 6 - networks

### 2024-07-09 ms_figure_6_networks.Rmd
Add Pho7 volcano plot (Fig 6)

---
title: "Figure 6 - networks"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    coords150: "data/visnetwork_coords_150_new.csv"
    rds500: "data/ipms_500_sce.rds"
    coords500: "data/visnetwork_coords_500_new.csv"
    rds150untag: "data/ipms_150_untag_sce.rds"
    interactors: "data/Gene_list_TFinteractors_Pombase20240226.txt"
    idmap: "data/id_mapping_table.txt"
    rad24_rad25_tbl: "data/FigS5_Rad24_Rad25_interactingTFs_list_motifs.txt"
editor_options: 
    chunk_output_type: console
---

@@

source("params/plot_settings.R")
source("params/get_testres_function.R")
source("params/mapping_functions.R")
```

@@

## Read table
set_flextable_defaults(font.size = 8)
rad24_rad25_tbl <- read.delim(params$rad24_rad25_tbl)[, 1:2] |>
    setNames(c("TF", "R-x-x-[S/T]-x-P")) |>
    dplyr::mutate(TF = .capitalize(TF))
stopifnot(all(gnames %in% rad24_rad25_tbl$TF))
ft <- flextable(rad24_rad25_tbl) |>
  width(width =  c(0.5, 1.25)) |>
  set_table_properties(layout = "fixed")
ggtbl <- ggplot() +
    theme_void() +
    annotation_custom(grid::rasterGrob(as_raster(ft)),
                      xmin = -Inf, xmax = Inf, ymin = 0, ymax = 1)

@@

@@

```{r Fig6}
#| fig.width: 10
#| fig.height: 10

@@

coords150 <- read.csv(params$coords150)
coords500 <- read.csv(params$coords500)
coords500$y <- -coords500$y

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none"), 
            ggr500 + theme(legend.position = "none"), 
            nrow = 1, labels = c("A", "B")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    cowplot::plot_grid(fig6c, ggrad_upset,
                       nrow = 1, labels = c("C", "D")), 
    rel_heights = c(5, 2), 
    ncol = 1
)
```

>>>>

---
title: "Figure 6 - networks"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    coords150: "data/visnetwork_coords_150.csv"
    rds500: "data/ipms_500_sce.rds"
    coords500: "data/visnetwork_coords_500.csv"
    rds150untag: "data/ipms_150_untag_sce.rds"
    interactors: "data/Gene_list_TFinteractors_Pombase20240226.txt"
    idmap: "data/id_mapping_table.txt"
    rad24_rad25_tbl: "data/FigS5_Rad24_Rad25_interactingTFs_list_motifs.txt"
editor_options: 
    chunk_output_type: console
---

@@

source("params/plot_settings.R")
source("params/get_testres_function.R")
source("params/mapping_functions.R")
source("params/ipms_params.R")
```

@@

## Read table
set_flextable_defaults(font.size = 8)
rad24_rad25_tbl <- read.delim(params$rad24_rad25_tbl)[, 1:2] |>
    setNames(c("TF", "R-x-x-[S/T]-x-P")) |>
    dplyr::mutate(TF = .capitalize(TF))
stopifnot(all(gnames %in% rad24_rad25_tbl$TF))
ftbl <- flextable(rad24_rad25_tbl) |>
  width(width =  c(0.5, 1.25)) |>
  set_table_properties(layout = "fixed")
ggtbl <- ggplot() +
    theme_void() +
    annotation_custom(grid::rasterGrob(as_raster(ftbl)),
                      xmin = -Inf, xmax = Inf, ymin = 0, ymax = 1)

@@

# Pho7 volcano plot

```{r}
md <- metadata(sce500)
volc <- md$testres$tests$Pho7_500_plate_vs_compl_Pho7_500_plate |>
    mutate(signif = adj.P.Val < adjpThreshold & logFC > log2fcThreshold)
(pho7volc <- ggplot(volc, aes(x = logFC, y = mlog10p)) + 
        geom_text_repel(data = volc |> filter(signif),
                        aes(label = pid), min.segment.length = 0,
                        max.overlaps = Inf) + 
        geom_point(aes(alpha = signif, color = signif), 
                   show.legend = c(alpha = FALSE, color = TRUE)) + 
        scale_color_manual(values = c(`TRUE` = main_colors[5], `FALSE` = na_color), 
                           labels = c(`TRUE` = paste0("adj. p < ", adjpThreshold, 
                                                      " and logFC > ", log2fcThreshold)),
                           na.value = "black", breaks = "TRUE") + 
        scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = 0.5)) + 
        geom_point(data = volc |> dplyr::filter(pid == "Pho7") |>
                       dplyr::mutate(type = "Bait"), 
                   mapping = aes(fill = type), color = main_colors[3], 
                   shape = 21, alpha = 1, size = 2) + 
        scale_fill_manual(values = c(Bait = main_colors[3])) + 
        labs(x = "log2(fold-change)", y = "-log10(p-value)", 
             title = "Pho7 vs complement (500 mM NaCl)") + 
        theme_cowplot(ft) + 
        theme(legend.position = "bottom") + 
        guides(color = guide_legend(nrow = 1, byrow = TRUE, title = ""),
               fill = guide_legend(nrow = 1, byrow = TRUE, title = "")))
```

@@

```{r Fig6}
#| fig.width: 10
#| fig.height: 12
#| warning: false

@@

coords150 <- read.csv(params$coords150)
coords500 <- read.csv(params$coords500)
coords150$y <- -coords150$y
coords500$y <- -coords500$y

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none"), 
            ggr500 + theme(legend.position = "none"), 
            nrow = 1, labels = c("A", "B")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    cowplot::plot_grid(
        cowplot::plot_grid(fig6c, ggrad_upset,
                           ncol = 1, labels = c("C", "D"),
                           rel_heights = c(1, 1.25)), 
        pho7volc, 
        nrow = 1, labels = c("", "E")
    ),
    rel_heights = c(5, 3.5), 
    ncol = 1
)
```
